Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/compilation.tex
unify syntax across paper

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \mapsto r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
     x       &::=& a.b.c.d/n & \textit{prefix} \\
     c       &::=& \cdots & \textit{community value} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \NOT t & \textit{negation} \\
         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
         &\BNFALT& \textit{comm} = c & \textit{community test} \\
     r       &::=& n & \textit{AS number} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

@@

  \caption{Example Product Graph IR construction for policy: $(W \cdot A \cdot C \cdot D \cdot out) \Prefer (W \cdot B \cdot in^* \cdot out)$.}
  \label{fig:example-compilation}
\end{figure*}

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(W \cdot A \cdot C \cdot D \cdot \Out) \Prefer (W \cdot B \cdot in^* \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates it is dropped from the corresponding automaton. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.

@@

To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures. For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
%
$$(W \cdot A \cdot C \cdot D) \Prefer (W \cdot B \cdot C \cdot E)$$
%
How could such a policy be implemented in BGP? Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$. However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.

@@

For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
$\CD{PG1} \mapsto \End(A)$, where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR. Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none. Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

>>>>

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
     x       &::=& a.b.c.d/n & \textit{prefix} \\
     c       &::=& \cdots & \textit{community value} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \NOT t & \textit{negation} \\
         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
         &\BNFALT& \textit{comm} = c & \textit{community test} \\
     r       &::=& n & \textit{AS number} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

@@

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
  \label{fig:example-compilation}
\end{figure*}

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates it is dropped from the corresponding automaton. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.

@@

To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures. For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
%
$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
%

How could such a policy be implemented in BGP? Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$. However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.

@@

For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR. Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none. Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).
